PAMELA: an annotation-based Java Modeling Framework

### 2021-01-27 1-Main.tex
Test
fix usepackage error
Started rebuttal process

\documentclass[sigchi]{acmart}

\usepackage[colorinlisttodo]{todonotes}

\usepackage{listings}
\usepackage{xcolor}

@@

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmlicensed}
\acmConference[Workshop XXX '2020]{A Workshop on Software Engineering}{2020}{Somewhere}
\acmBooktitle{Workshop XXX '2020: Workshop on Software Engineering, Somewhere}
%\acmPrice{15.00}
%\acmDOI{10.1145/1122445.1122456}
%\acmISBN{978-1-4503-9999-9/18/06}

\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{PAMELA: an annotation-based Java Modelling Framework}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Sylvain Guérin, Guillaume Polet, Caine Silva, Joel Champeau}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{Lab-STICC \\ ENSTA Bretagne}
%  \streetaddress{P.O. Box 1212}
  \city{Brest}
  \country{France}
  %  \postcode{43017-6221}
}
\email{firstname.lastname@ensta-bretagne.fr}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{S. Guérin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Model-Driven Engineering, Java Modelling Framework, Meta-modeling, Models@Runtime}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\input{3-Introduction}

\input{4-ApproachOverview}

\input{5-Features}

\input{6-Experimentations}

\input{7-Relatedworks}

@@

>>>>

%\documentclass[preprint]{acmart}
\documentclass[preprint]{elsarticle}
\journal{Science of Computer Programming}

%\usepackage[colorinlisttodo]{todonotes}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tikz-uml}

@@

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2https://www.overleaf.com/project/5efee0e8ad6bc10001d47854
}

@@

%\acmPrice{15.00}
%\acmDOI{10.1145/1122445.1122456}
%\acmISBN{978-1-4503-9999-9/18/06}

\begin{document}
\begin{frontmatter}

\title{PAMELA: an annotation-based Java Modeling Framework}

%% Group authors per affiliation:
%\author{Sylvain Guérin, Guillaume Polet, Caine Silva, Joel Champeau}
%\address{ENSTA Bretagne}

%\author{Jean-Christophe Bach, Salvador Martinez, Antoine Beugnard}
%\address{IMT Atlantique}

%% or include affiliations in footnotes:
\author[mymainaddress]{Sylvain Guérin\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author[mymainaddress]{Guillaume Polet}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author[mymainaddress]{Caine Silva}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author[mymainaddress]{Joel Champeau}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author[mysecondaryaddress]{Jean-Christophe Bach}
%\ead{firstname.lastname@imt-atlantique.fr}

\author[mysecondaryaddress]{Salvador Mart\'inez}
%\ead{firstname.lastname@imt-atlantique.fr}

\author[mysecondaryaddress]{Antoine Beugnard}
%\ead{firstname.lastname@imt-atlantique.fr}

\address[mymainaddress]{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}%vérifier si c'est l'affiliation officielle
\address[mysecondaryaddress]{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}

@@

\begin{keyword}
Model Driven Engineering \sep Object Oriented Programming \sep Metaprogramming 
\end{keyword}

\end{frontmatter}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

\section{Introduction}
\label{sec:introduction}
\input{introduction.tex}

\section{Approach}
\label{sec:pamproc}
\input{pamelaProcess.tex}

\section{Software Framework and Features}
\label{sec:architecture}
\input{architecture.tex}

\section{Implementation}
\label{sec:implementation}
\input{implementation.tex}

%\section{Industrial experimentation and validation}
%\label{sec:validation}
%\input{validation.tex}

\input{6-Experimentations}
\label{sec:Experimentations}

\section{Related Work}
\label{sec:related}
\input{related.tex}

%\input{4-ApproachOverview}

%\input{5-Features}

%\input{6-Experimentations}

%\input{7-Relatedworks}

@@

% Prout
